Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-01-28 CAV 2025 TODO/experiments.tex
exp

%The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
To measure the impact of the scoring function to select neurons to open, 
we considered the largest complex CNN-B-Adv, with 20 000 nodes. 
We tested over the $\vx=37$th image in the CIFAR dataset.
To measure the accuracy, we measure the uncertainty of all nodes in the 4th layer:
the uncertainty of a node is the range between its computed lower and upper bound. 
We then average the uncertainty among all the nodes of the layer.
Formally, the uncertainty of a node $a$ with bounds $[\LB,\UB]$ is uncert$(a) = \UB - \LB$. The average uncertainty of layer $\ell$ is $\dfrac{\sum_{a\in l} \text{uncert}(a)}{size(\ell)}.$

@@

Overall, SAS is more accurate than GS, more accurate than Huang, more accurate than random choice of variables. SAS significantly outperforms other solutions, 
with around 3 times less binary variables for the same accuracy (10 v 30, 6 vs 16).
Each individual node of the last layer display a similar pattern, and the pattern is similar for different images (not displayed).

We also experimented on fixing an ordering on variable in Gurobi, with a fixed selection of nodes by SAS. Indeed, Gurobi relies on a BaB procedure to compute bounds. The standard Gurobi procedure is adaptative in each branch. We compared vs the fix order provided by SAS, as well as the fixed order provided by FSB, for both accuracy and runtime (lower is better).

We obtained the following:
Gurobi order:
30nodes : 1, 3.987387317631171, 260.4883162975311, 
45nodes : 1, 4.015747873604205, 265.53007888793945, 
60nodes : 1, 4.053423060042739, 262.1407461166382,

FSB order:
30nodes : 1, 3.9879578118285317, 246.69000577926636, 
45nodes : 1, 4.018561938508719, 247.65485453605652
60nodes : 1, 4.032634363809192, 247.81136560440063,

SAS order:
30nodes : 1, 3.9933637922653995, 264.4269104003906, 
45nodes : 1, 4.0307741092892035, 266.20811343193054, 
60nodes : 1, 4.060220618788057, 262.93414759635925,

>>>>

%The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
To measure the impact of the scoring function to select neurons to open, 
we considered the largest complex CNN-B-Adv, with 20 000 nodes. 
We tested over the $\vx=37$th image in the CIFAR dataset.
To measure the accuracy, we measure the uncertainty of all nodes in the 4th layer:
the uncertainty of a node is the range between its computed lower and upper bound. 
We then average the uncertainty among all the nodes of the layer.
Formally, the uncertainty of a node $a$ with bounds $[\LB,\UB]$ is uncert$(a) = \UB(a) - \LB(a)$. The average uncertainty of layer $\ell$ is 
$$\dfrac{\sum_{a\in l} \text{uncert}(a)}{size(\ell)}.$$

@@

Overall, SAS is more accurate than GS, more accurate than Huang, more accurate than random choice of variables. SAS significantly outperforms other solutions, 
with around 3 times less binary variables for the same accuracy (10 v 30, 6 vs 16).
Each individual node of the last layer displays a similar pattern, and the pattern is similar for different images (not displayed).

We also experimented in Table \ref{table.order} on fixing an ordering on variable in Gurobi, with a fixed selection of nodes by SAS. Indeed, Gurobi relies on a BaB procedure to compute bounds. The standard Gurobi procedure is adaptative in each branch. We compared vs the fix order provided by SAS, as well as the fixed order provided by FSB, for both accuracy and runtime (lower is better).

\begin{table}[h!]	
	\centering
	\begin{tabular}{|c||c c|c c|c c|}
		\hline
		  & \multicolumn{2}{c|}{30 open ReLUs} & \multicolumn{2}{c|}{45 open ReLUs} & \multicolumn{2}{c|}{60 open ReLUs} \\ 
		 order & uncert & time & uncert & time & uncert & time \\
		\hline \hline
		Gurobi &   3.987  & 260s  & 4.016 & 266s& 4.053 & 262s\\ 
		SAS &   3.989  & 264s  & 4.031 & 266s& 4.060 & 263s\\
		FSB &   3.988  & {\bf 246s}  & 4.018 & {\bf 248s}& 4.033 & {\bf 248s}\\ \hline
	\end{tabular}
	\caption{Comparison of different ordering with selection of ReLUs by SAS.}
	\label{table.order}
	%\vspace{-0.6cm}
\end{table}
